---
title: "Homework 1"
author: "Sara Burpeau"
date: "February 3, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1

```{r mh_distance_function}
mh_distance <- function(x, y){
  if (typeof(x) != typeof(y)){
    warning("x and y different vector types")
    return(-1)
    }
  if(is.na(x) == TRUE || is.na(y) == TRUE || 
     is.nan(x) == TRUE || is.nan(y) == TRUE){
    warning("x or y is NA or NaN")
    return(-1)
  }
  if(is.infinite(x) == TRUE || is.infinite(y) == TRUE){
    warning("x or y is an infinite value")
    return(-1)
  }
  if ((nchar(x) != nchar(y)) 
      & (typeof(x) != "logical")){
    warning("x and y do not have the same number of digits or letters")
    return(-1)}
  if ((is.numeric(x) == TRUE) & (is.numeric(y) == TRUE)){
    if ((x %% 1 != 0) || (y %% 1 != 0)){
      warning("x or y contains a decimal")
      return(-1)
    }
  }
  if (typeof(x) == "character"){
    x_list = strsplit(x, "")
    y_list = strsplit(y, "")
    x_vector = unlist(x_list)
    y_vector = unlist(y_list)
    number = x_vector != y_vector
    return(sum(number, na.rm = TRUE))
    }
  if (typeof(x) == "double"){
    xchar = toString(x)
    ychar = toString(y)
    x_list = strsplit(xchar, "")
    y_list = strsplit(ychar, "")
    x_vector = unlist(x_list)
    y_vector = unlist(y_list)
    number = x_vector != y_vector
    return(sum(number, na.rm = TRUE))
    }
  if (typeof(x) == "logical"){
    if (((x == TRUE) & (y == TRUE)) || ((x == FALSE) & (y == FALSE))){
      return (0)
      }
    else{
      return(1)
    }
  }
}
```

## Task 2

**Initial test cases** (return a non-negative modified Hamming distance)

```{r provided-correct-tests}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r correct-test-cases}
mh_distance(x = 52, y = 43)
mh_distance(x = "snack", y = "stash")
mh_distance(x = TRUE, y = TRUE)
mh_distance(x = "Hello!", y = "Hello?")
```

**Initial test cases** (return values of `-1`)

```{r provided-incorrect-tests}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r incorrect-test-cases}
mh_distance(x = 78, y = 78.9)
mh_distance(x = "fishy", y = "fishes")
mh_distance(x = NA, y = NaN)
mh_distance(x = -Inf, y = Inf)
```


## Task 3

Consider the pair of vectors `s` and `w` given below.

```{r define-vectors}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
```

```{r vectorized-mh-distance}
mh_distance_vectorize <- function(a, b){
  for(i in 1:length(a)){
    if(nchar(a[i]) == nchar(b[i])){
      print(paste0("The modified Hamming distance between ", a[i], " and ", b[i],
             " is ", mh_distance(a[i], b[i])))
    }
  }
}
```

```{r test-vectorized}
mh_distance_vectorize(s, w)
```

## Task 4

This homework assignment was a bit challenging, but after some initial struggle,
I managed to get the hang of it. To handle invalid inputs, I used if statements
with warning messages. Throughout writing my code, one of my biggest challenges
was keeping track of parentheses to ensure I would not run an error. In creating
my code, I used the strsplit() function to break apart words/numbers into
individual components to compare inputs. I then unlisted them to turn each word
into a vector of its letters.

Initially, I planned to use a for loop to compare each input. I had a hard
time getting this to work however and continued to use if statements instead.
At first, the function worked fine with characters and boolean values. I had
the most trouble when comparing doubles. For some reason, they would always
output -1 instead of the correct modified Hamming distance but without an error
message. I restarted the entire code going step by step and ran it again. This
time it worked! Not really sure what was different, but I'm running with it! 
My code could be improved during the section where I compare each character in
x to its corresponding character in y. I think this area could be simplified
with a for loop or the use of some different functions.

