---
title: "Homework 1"
author: "Sara Burpeau"
date: "February 3, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1

```{r mh_distance_function}
mh_distance <- function(x, y) {
  if(typeof(x) != typeof(y)){
    warning("x and y different vector type")
    return(-1)
  }
  if(as.NA(x) | as.NA(y) | as.NaN(x) | as.NaN(y)){
    warning("x or y NA or NaN")
    return(-1)
  }
  if(nchar(x) != nchar(y)){
    warning("x and y different character lengths")
    return(-1)
  }
  if(as.infinite(x) | as.infinite(y)){
    warning("x or y infinite value")
    return(-1)
  }
  if("." %in% as.numeric(x) | "." %in% as.numeric(y)){
    warning("x or y contains decimal value")
    return(-1)
  }
  x <- unlist(strsplit(x, split = ""))
  y <- unlist(strsplit(y, split = ""))
  x == y
  mhd <- sum(TRUE)
  return(mhd)
}
```

# is.finite, is.infinite


## Task 2

<i>
Be sure to remove chunk option `eval=FALSE` in the below code chunks
once you create `mh_distance()`. Do not include this italicized
text in your final submission.
</i>

**Initial test cases** (return a non-negative modified Hamming distance)

```{r eval=FALSE}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r}
# additional test cases go here
```

**Initial test cases** (return values of `-1`)

```{r eval=FALSE}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r}
# additional test cases go here
```


## Task 3

Consider the pair of vectors `s` and `w` given below.

```{r}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
```

```{r}
# loop goes here
```


## Task 4

Brief write-up goes here...
